\documentclass[a4paper]{article}

%% Language and font encodings
\usepackage[english]{babel}
\usepackage[utf8x]{inputenc}








\begin{document}
\title{Dictionary of software application}

\author{Mingyu Zhang,Yufei Zeng}
\maketitle

\textbf{Problem statement: What software could do?}\newline
As a Computer Science major, I am attracted by the computer’s abilities to compute massive data and to accomplish lots of amazing things, and I hope to start some projects on my own time. I try to get some idea by looking at different software engineering project online, but I only get pieces of information about some application project and some usage of new technology like machine learning, What I want to find is a place that contains software applications from all kinds of fields and to find which one I feel most interested, but I didn’t get too much. Software is needed applied to every possible filed, and most people, even as a programmer, are only familiar with few daily used part, like web page, which I think it is a problem that is important and is easy to solve.
 \newline
 \newline
\textbf{Why it is important: It helps to build program}\newline
For a programmer, the job mostly does is related to algorithm, or program. An algorithm has two major components, the first one is the skill set, such as programming language, to implement a program, the second one is the abstract model to guild the program. The first one is relatively easy to have, people could learn it everywhere, from college or some great web sources. The second one needs more creativity and hand-on experience to understand the problem that will be solved by a program, then to make a model about it. Most software focus on a specific field, like the text processor, and programmer, who makes algorithm out of it, not only needs to be able to write a program but also needs to have a deeply understand about it and then make a model, which takes longer time to finish. I have written a program about Hanoi Tower, and it takes me hours to try to figure out a way to form the program and I get no lead because I never heard it before and have no idea how to solve it, then I find some clues from a website about how to solve it by hand and It only takes me 30 minutes to program it.
Like writing a paper, the more you know the object, the better paper you get. Knowing software application in different fields and choice one or few to focus on would gives more time to be familiar with the problem and helps make a better program.
\newline
 \newline
\textbf{Solution:A Website and Platform} 
This problem is mainly caused by lacking the access of relevant information, and build a website is one of the best solution for such problem because it has several unique features. First, the information in a web page is easy to access, visitors could access the content anytime and anywhere through phone or laptop, and do not need a heave book. Second, webpage has some advantages for showing information compare to book, it has hyperlink to jump to necessary pages and search box to find correct content, which help the reader quickly find needed information. Third, it is easy to maintain and upload huge amount of data. A webpage could easily hold huge amount of data and allows upload new content anytime, also webpage as a flexible tool to display information is a perfect match for such requirement.
 \newline
 \newline
 \newline
\textbf{What’s new}\newline
Usually, information about software application is make for a specific project, a website specifically designed for this propose would display a collection of such information about all involved fields, and this website is served as dictionary to help the reader get information and gives an overview of all software usage.
Also, such information is given by the author for a specific project instead of whole fields, which didn’t give a clear picture about how the software is used there, a website could include both information and uses the specific project as a subset of one field. And this webpage not only allows manager constantly to modify and to update its content but also allows viewer to add new content or post feedback or personal experience, which very like a small platform or Wikipedia. The content created by viewer will be a good complement for the website.
 \newline
 \newline
\textbf{Cost and Difficulty}\newline
For the technic part, to build the layout of the webpage is not complex, but because of the huge amount of data, the database’s management would be difficult, also if there is large amount of viewer, it needs to rent some server to support the webpage. All this require skilled staff to work on the page, so it is better to have an experienced web developer to guild the object. Also, it will spend some money to build the webpage at first, but the cost will lower to reasonable range later.
And for the content, because it about information in wild range and has huge amount, it takes lots of effect to make the content. Like Wikipedia, this webpage could allow viewer to upload content, and it will largely reduce the effect needed for the worker of the website.
 \newline
 \newline
\textbf{Risk and Possible Problem}\newline
First, this project is quite large because of the very huge amount of information it involved, which means it will take lots of money and effect to build it, but this is no guarantee that people would like it. So, it better starts with smaller range of fields to test if some people would interest in.
Second, the information displayed in the webpage would not be fully objective, and there is no such standard to guild the process. This could partly solved by allowing every interested people to post idea about certain part, and this would gives the viewer a overall understanding from different angle.


\end{document}

